---
output:
  rmarkdown::github_document
# bibliography: "README-refs.bib"
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# R/`LtAtStructuR`

> Structuring of Complex Longitudinal Data into Long Format

__Authors:__ [Romain
Neugebauer](https://divisionofresearch.kaiserpermanente.org/researchers/neugebauer-romain), Noel Pimentel, and Nima Hejazi

---

## What's `LtAtStructuR`?

The goal of `LtAtStructuR` is to structure a collection of time-stamped
measurements (e.g., electronic health record data)  into a standard long format
analytic dataset suitable for the evaluation of the effect of multiple
time-point interventions in the presence of time-dependent confounding or
sources of selection bias.

---

## Installation

Download the `LtAtStructuR` directory and install the package from the command
line using

```{bash cmdline-source-install, eval=FALSE}
R CMD INSTALL LtAtStructuR
```

or from within R using the package tarball (`.tar.gz`) with

```{r r-source-install, eval=FALSE}
install.packages("PATH/TO/LtAtStructuR_version.tar.gz", type = "local")
```
where the path to the package tarball and version number must be amended. A
tarball may be generated by invoking either of `make build` or `make buildfast`
from the root directory of this project.

---

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval=FALSE}
library(LtAtStructuR)
library(data.table)
library(lubridate)
library(future) # optional (for parallel processing)
plan(multiprocess) # optional (for parallel processing)

## Define one cohort dataset, one exposure dataset, and one or more covariate
## datasets
cohort <- setCohort(cohortDT, "ID", "IndexDate", "EOFDate", "EOFtype",
                    "AMI", c("ageEntry", "sex", "race", "A1c", "eGFR"),
                    list("ageEntry"=list("categorical"=FALSE,
                                        "impute"=NA,
                                        "impute_default_level"=NA),
                        "sex"=list("categorical"=TRUE,
                                   "impute"=NA,
                                   "impute_default_level"=NA),
                        "race"=list("categorical"=TRUE,
                                    "impute"=NA,
                                    "impute_default_level"=NA)) )
exposure <- setExposure(expDT, "ID", "startA", "endA")
covariate1 <- setCovariate(a1cDT, "sporadic", "ID", "A1cDate", "A1c",
                           categorical = FALSE)
covariate2 <- setCovariate(egfrDT, "sporadic", "ID", "eGFRDate", "eGFR",
                           categorical = TRUE)

## Gather each input dataset into a single object that specifies the content of
## the output dataset to be constructed
LtAt.specification <- cohort + exposure + covariate1 + covariate2

## Construct the output dataset
LtAt.data <- construct(LtAt.specification, time_unit = 15, first_exp_rule = 1,
                       exp_threshold = 0.75)
```

---

## License

&copy; 2019 [Romain S. Neugebauer](https://divisionofresearch.kaiserpermanente.org/researchers/neugebauer-romain)

The contents of this repository are distributed under the GPL-3 license. See
file `LICENSE` for details.

